Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-08 tests-aniso-conduct.tex
Clarifying the streamlines in the aniso conduction plot.

\begin{figure}
\begin{center}
\includegraphics[width=0.42\textwidth]{figures/aniso_conduction_initial_output.eps}
\includegraphics[width=0.42\textwidth]{figures/aniso_conduction_final_output.eps}
\caption{Two-dimensional anisotropic conduction test in a uniform,
constant temperature background with circular magnetic fields centered
on (0.5, 0.5) in a $256 \times 256$ grid. The background medium has a
density of 1 proton/cc and a temperature of $10^6$~K.  At t$ = 0$
(left panel), a Gaussian heat pulse is injected at (0.75, 0.5) with a
FWHM of $1/64$ (with all numbers given in units of the box size) and a
peak temperature of $10^8$~K, and allowed to evolve without
hydrodynamical motion (i.e., static gas) and no radiative cooling for
300 Myr.  At t$ = 300$~Myr (right panel), heat has been transported
along magnetic field lines with no significant diffusion perpendicular
to field lines. Furthermore, there are no detectable oscillations in
the temperature in regions where the magnetic field is not parallel
with the grids.}
\label{fig.conduct}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.42\textwidth]{figures/aniso_conduction_initial_output.eps}
\includegraphics[width=0.42\textwidth]{figures/aniso_conduction_final_output.eps}
\caption{Two-dimensional anisotropic conduction test in a uniform, constant
temperature background with circular magnetic fields (indicated by white
streamlines) centered on (0.5, 0.5) in a $256 \times 256$ grid. The background
medium has a density of 1 proton/cc and a temperature of $10^6$~K.  At t$ = 0$
(left panel), a Gaussian heat pulse is injected at (0.75, 0.5) with a FWHM of
$1/64$ (with all numbers given in units of the box size) and a peak
temperature of $10^8$~K, and allowed to evolve without hydrodynamical motion
(i.e., static gas) and no radiative cooling for 300 Myr.  At t$ = 300$~Myr
(right panel), heat has been transported along magnetic field lines with no
significant diffusion perpendicular to field lines. Furthermore, there are no
detectable oscillations in the temperature in regions where the magnetic field
is not parallel with the grids.}
\label{fig.conduct}
\end{center}
\end{figure}
